---
title: "Lomas Barbudal Interactive Map"
author: "Brendan Barrett"
date: "7/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(sf)
library(sp)
library(stringr)
library(parzer)
library(janitor)
library(mapview)
library(rgdal)
```

## Identifying Lomas Sleepsites

This is an interactive map to use historical written records to identify Lomas sleepsites to a grid system. This website has 2 grids. One in yellow is a 100 meter grid. The orange grid is a 50 m grid. Landmarks (i.e. rios, trails, waypoints) are color coded with legend on right. On the left, the images with stacked layers can be clicked to turn on and off layers of toggle between map types (i.e. topographic map, open street map, satelite imagery).

I recommend turning off both grids initially, as this layer can make interface clunky, and to identify sleepsite using relvant landmarks. If you click on a feature, you can see its name and corresponding information.

When you have identified where you think the sleepsite is, turn on the grid. When you scroll over a grid a unique id should pop up. That id, for both grids should be entered into the historical sleepsite CSV, saved, and backed up to github.We can set this up later.

```{r code setup, echo=FALSE , include=FALSE}

#read file from local source

fname <- "/Users/BJB/Dropbox/ODD_GPSwork/susan_sleepsite_map/Common Sleep Sites.csv" #this will need to be changd to your folder

g <- st_read(fname , package='sf')
str(g)
g$latlong <- as.character(g$LAT...LONG) #convert to string
g$latitude <- str_sub(g$latlong,1,10) #extract lat
g$longitude <- str_sub(g$latlong,-10,-1) #extract long
g <- g[ , c("WPT.NAME","COMMON.NAMES", "latitude", "longitude" , "ELEV") ] #subset
g <- clean_names(g)#make names better
g$latitude <- parse_lat(g$latitude)#convert to decimal coords
g$longitude <- parse_lon(g$longitude)#convert to decimal coords
g$elev <- as.numeric(str_sub(g$elev,1,3))/3.28084 #convert to meters
g2 <- st_as_sf(g, coords=c("longitude", "latitude"), crs = 4326) 

#convert to sf object
sleepsites <- st_as_sf(g, coords=c("longitude", "latitude"), crs = 4326) #convert to sf object
#mapview(g2) + mapview(trails)

POIs <- readOGR(dsn = "/Users/BJB/Dropbox/ODD_GPSwork/susan_sleepsite_map/Lomas Barbudal Map POI.GPX", layer="waypoints") 


# Identify shapefiles
working_dir = "~/Dropbox/LOMAS_MAP/QGIS/1.4/shapefiles/" #this could be your local file with lomas map
setwd(working_dir)
shapefiles = list.files(pattern = "shp$", recursive = TRUE) #get all shape files names
str(shapefiles)

trailsshp <- shapefiles[grepl('Trails/', shapefiles, fixed = TRUE)] 
riossshp <- shapefiles[grepl('Rios/', shapefiles, fixed = TRUE)] 
quebsshp <- shapefiles[grepl('Quebradas/', shapefiles, fixed = TRUE)] 
canalshp <- shapefiles[grepl('Canal/', shapefiles, fixed = TRUE)] 
drtrdshp <- shapefiles[grepl('Dirt Roads/', shapefiles, fixed = TRUE)] 
dryquebshp <- shapefiles[grepl('Dry Quebradas/', shapefiles, fixed = TRUE)] 
fenceshp <- shapefiles[grepl('Fences/', shapefiles, fixed = TRUE)] 
majrdsshp <- shapefiles[grepl('Major Roads/', shapefiles, fixed = TRUE)] 
shtctsshp <- shapefiles[grepl('Shortcuts/', shapefiles, fixed = TRUE)] 


#make a spatial object of trails, can do the same for other stuff if desired

for (i in 1:length(trailsshp)){
  shpi <- readOGR(dsn = paste0(working_dir,trailsshp[i])) 
  if(i==1){trails <- shpi}
  if(i>1){trails <- rbind(trails,shpi)}
}

for (i in 1:length(riossshp)){
  shpi <- readOGR(dsn = paste0(working_dir,riossshp[i])) 
  if(i==1){rios <- shpi}
  if(i>1){rios <- rbind(rios,shpi)}
}

for (i in 1:length(quebsshp)){
  shpi <- readOGR(dsn = paste0(working_dir,quebsshp[i])) 
  if(i==1){quebradas <- shpi}
  if(i>1){quebradas <- rbind(quebradas,shpi)}
}

for (i in 1:length(dryquebshp)){
  shpi <- readOGR(dsn = paste0(working_dir,dryquebshp[i]))
  if(i==1){dry_quebradas <- shpi}
  if(i>1){dry_quebradas <- rbind(dry_quebradas,shpi)}
}

for (i in 1:length(fenceshp)){
  shpi <- readOGR(dsn = paste0(working_dir,fenceshp[i])) 
  if(i==1){fences <- shpi}
  if(i>1){fences <- rbind(fences,shpi)}
}

for (i in 1:length(majrdsshp)){
  shpi <- readOGR(dsn = paste0(working_dir,majrdsshp[i])) 
  if(i==1){major_roads <- shpi}
  if(i>1){major_roads <- rbind(major_roads,shpi)}
}

for (i in 1:length(drtrdshp)){
  shpi <- readOGR(dsn = paste0(working_dir,drtrdshp[i])) 
  if(i==1){dirt_roads <- shpi}
  if(i>1){dirt_roads <- rbind(dirt_roads,shpi)}
}

all_shapes <- rbind(trails,rios,quebradas,fences,dry_quebradas,dirt_roads, major_roads)
#mapview(all_shapes)
quebsshp
#mapview(trails) + mapview(rios) +  mapview(quebradas)

#######brendans map

grid_shapes <- rbind(trails,rios,quebradas,fences,dry_quebradas,dirt_roads)
#mapview(grid_shapes)

bbbb <- st_as_sf(grid_shapes)

gridtest <- st_make_grid(bbbb, square = T, cellsize = c(1000, 1000) ) %>% st_sf() 

#mapview(gridtest)
grid_500m <- st_make_grid(gridtest, square = T, cellsize = c(500, 500) ) %>% 
  st_sf() 

grid_100m <- st_make_grid(gridtest, square = T, cellsize = c(100, 100) ) %>% 
  st_sf() 

grid_50m <- st_make_grid(gridtest, square = T, cellsize = c(50, 50)) %>% # the grid, covering bounding box
  st_sf() # not really required, but makes the grid nicer to work with later


```

## Lomas Barbudal Interactive Map (v 0.1)


```{r interactive map, echo=FALSE , fig.height = 8, fig.width = 10 , message=FALSE}
mapview(grid_100m , alpha.regions = 0.01 , color="yellow" , lwd=1 , col.regions="yellow") + mapview(grid_50m , alpha.regions = 0.01 , color="orange", col.regions="orange")  + mapview(trails , color="red") +  mapview(major_roads , color="grey") + mapview(dirt_roads , color="brown") + mapview(fences , color="black") +  mapview(rios , color="darkblue" , lty=3) +  mapview(quebradas , color="blue") + mapview(dry_quebradas , color="lightblue" , lw=0.5) + mapview(sleepsites, color="green" , col.regions="green" , cex=3 ) + mapview(POIs , color="violet", col.regions="violet" , cex=3)
```
